Data Analysis Expanded

### 2019-08-27 data_analysis/data_analysis_expanded.Rmd
Slight change to m3s3

```{r s1_m1_d}

set.seed(2339)
s1_m1_d <- rre::minimum_subset_distance(list_of_samples[[1]],
                                        partitions = 10,
                                        lambda_vec = 700:740,
                                        multiplier = 2,
                                        c_seq_len = 11,
                                        starts = data.frame(alpha = 0.28863,
                                                            delta = 0.0032607))
```
```{r s1_m1_d_print, results = 'asis'}
s1_m1_d %>% report_results_2(.,  list_of_samples[[1]], report_eta = T)
```
<br><br>

@@

```{r s3_m1_d}
set.seed(452348)
s3_m1_d <- rre::minimum_subset_distance(list_of_samples[[3]],
                                        partitions = 10,
                                        lambda_vec = seq(500, 600 ,by=5),
                                        multiplier = 2,
                                        c_seq_len = 11,
                                        starts = data.frame(alpha = 0.5143,
                                                            delta = 0.003997))
```
```{r s3_m1_d_print, results = 'asis'}
s3_m1_d %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br>

@@

For each method and sample we save the most refined or best estimate.
```{r output_data}
sample_1 <- list(method_0 = s1_m0_b$best,
                 method_1 = s1_m1_d$best,
                 method_2 = s1_m2_c$best,
                 method_3 = s1_m3_d$best,
                 method_4 = s1_m4_b$best)

>>>>

<!--
```{r s1_m1_d}
# This seemed like a good idea until realizing how long it would take to do all the methods to this level of precision:

#set.seed(2339)
#s1_m1_d <- rre::minimum_subset_distance(list_of_samples[[1]],
#                                        partitions = 10,
#                                        lambda_vec = 700:740,
#                                        multiplier = 2,
#                                        c_seq_len = 11,
#                                        starts = data.frame(alpha = 0.28863,
#                                                            delta = 0.0032607))
```
```{r s1_m1_d_print, results = 'asis'}
#s1_m1_d %>% report_results_2(.,  list_of_samples[[1]], report_eta = T)
```
<br><br>
-->

@@

```{r s3_m1_d}
# Previous result on the edge of lambdagrid
set.seed(452348)
s3_m1_d <- rre::minimum_subset_distance(list_of_samples[[3]],
                                        partitions = 10,
                                        lambda_vec = seq(450, 550 ,by=5),
                                        multiplier = 2,
                                        c_seq_len = 11,
                                        starts = data.frame(alpha = 0.5143,
                                                            delta = 0.003997))
```
```{r s3_m1_d_print, results = 'asis'}
s3_m1_d %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br>

@@

For each method and sample we save the most refined or best estimate.
```{r output_data}
sample_1 <- list(method_0 = s1_m0_b$best,
                 method_1 = s1_m1_c$best,
                 method_2 = s1_m2_c$best,
                 method_3 = s1_m3_d$best,
                 method_4 = s1_m4_b$best)
